The Impact of Educational Expenses of New Coders

### 2021-04-18 outputs/paper/paper.Rmd
Add data collection

With an increasing interest in computer programming and the growth of coding related jobs, more and more people invest their time and money in taking programming courses [@citeHughes]. In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time. The dataset used for this paper is obtained from freeCodeCamps GitHub page ^[https://github.com/freeCodeCamp/2017-new-coder-survey]. Approximately 20,000 beginner programmers had participated in the survey [@citeSurvey2017].

@@

@@

```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
#### A partial view of the cleaned dataset ####
tabCleanedData <-
  dfNewCoders[1:10,] %>%
  mutate_all(linebreak) %>%
  kable(caption = "A partial view of \\\\the cleaned dataset",
      booktabs = T,
      escape = F,
      "latex",
      col.names = linebreak(c("Gender", 
                              "Age",
                              "City\nPopulation",
                              "Commute\nTime",
                              "Income",
                              "Months\nProgramming",
                              "School\nDegree",
                              "Money For\nLearning"), align = "c")) %>%
  kable_classic(full_width = F)

@@

>>>>

With an increasing interest in computer programming and the growth of coding related jobs, more and more people invest their time and money in taking programming courses [@citeHughes]. In this paper, I examine some of the factors that may affect educational expenses of new coders or entry-level programmers aside from university tuition, mainly focusing on the level of education, the size of city, commuting time, income, and learning time. Approximately 20,000 beginner programmers had participated in the survey [@citeSurvey2017].

@@

```
## Data Collection
The survey was run by `freeCodeCamp`, a non-profit organization that helps people learn to code through their free online courses and build a network for their alumni [@citeAbout]. The purpose of the survey was to examine how the users learn to code [@cite2017Survey]. The survey was conducted over the internet, and the survey respondents were limited to those persons with less than 5 years learning programming; all the respondents were asked whether they have already been coding for more than 5 years or not before starting the survey [@cite2017Survey]. The survey is composed of 48 questions and takes about five minutes to complete, and the survey results are under the Open Data Common License, which can be freely distributed through the organization’ GitHub repository [@cite2017Survey].^[https://github.com/freeCodeCamp/2017-new-coder-survey]

@@

```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
#### A partial view of the cleaned dataset ####
tabCleanedData <-
  dfNewCoders[1:10,] %>%
  mutate_all(linebreak) %>%
  kable(caption = "A partial view of the cleaned dataset",
      booktabs = T,
      escape = F,
      "latex",
      col.names = linebreak(c("Gender", 
                              "Age",
                              "City\nPopulation",
                              "Commute\nTime",
                              "Income",
                              "Months\nProgramming",
                              "School\nDegree",
                              "Money For\nLearning"), align = "c")) %>%
  kable_classic(full_width = F)

@@

Table \@ref(tab:tabDescrStat) is
